---
title: "Q1 models"
format:
  html: 
    code-fold: true
editor: visual
---

## Analysis

In this part we will attempt to answer our research questions by analysing our graphs, and making regression models.

### Q1. Which physical factors have the biggest impact on used car prices?

Our dependant variable will be price. We will make a regression model that includes all of our variables then do a stepwise regression (backward) to remove non significant variables, in order to find the optimal model.

```{r, message=FALSE, warning=FALSE}
# Libraries + datasets

library(tidyverse)
library(plotly)
library(corrplot)
library(Hmisc)
library(car)
library(MASS)
setwd("~/GitHub/Data_science/cleaned-data")
golf <- read.csv("golf2_cleaned.csv")
audi <- read.csv("audi2_cleaned.csv")
skoda <- read.csv("skoda2_cleaned.csv")
volvo <- read.csv("volvo2_cleaned.csv")
toyota <- read.csv("toyota_cleaned.csv")
```

We will first have a look at the variables vehicle.age and kilometers, which we think will have the greatest impact on prices, to make sure the errors are linear. Below are the residuals vs fitted values plots of our 5 car models, for a simple linear regression of vehicle.age on price.

::: panel-tabset
### VW Golf

```{r, message=FALSE, warning=FALSE}
# golf
ggplot(lm(golf$price ~ golf$vehicle.age), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Audi A3

```{r, message=FALSE, warning=FALSE}
# audi
ggplot(lm(audi$price ~ audi$vehicle.age), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Skoda Octavia

```{r, message=FALSE, warning=FALSE}
# skoda
ggplot(lm(skoda$price ~ skoda$vehicle.age), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Volvo XC60

```{r, message=FALSE, warning=FALSE}
# volvo
ggplot(lm(volvo$price ~ volvo$vehicle.age), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
# toyota
ggplot(lm(toyota$price ~ toyota$vehicle.age), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```
:::

The relationship between price and vehicle age is obviously not linear. The blue line that represents the residuals should be more horizontal to resemble the red fitted values line. We can see this when we plot both variables with a linear method vs a loess method.

::: panel-tabset
### Linear model

```{r, message=FALSE, warning=FALSE}
ggplot(golf, aes(vehicle.age, price)) + 
  geom_point() +
  geom_smooth(method = lm) +
  ylim(0, max(golf$price))
```

### LOESS

```{r, message=FALSE, warning=FALSE}

ggplot(golf, aes(vehicle.age, price)) + 
  geom_point() +
  geom_smooth(method = loess) +
  ylim(0, max(golf$price))
```
:::

In the graph above for the VW Golf, we can see that the average price goes up after a vehicle age of approx. 9000 days (= 24 years, 7 months, 21 days) which is counter-intuitive. One hypothesis would be that these cars could be considered as vintage or collector cars, and therefore won't appeal to the average buyer, who is a daily driver. These types of cars have usually been very well maintained and have low mileage, which could also explain this overvaluation. We also notice that the curve is steeper and therefore cars seem to depreciate faster in their first 2500 days (6 years, 10 months, 2 days) than in their next 7500 (20 years, 6 months, 12 days).

We repeat the process but replace vehicle.age by kilometers and notice similar results.

::: panel-tabset
### VW Golf

```{r, message=FALSE, warning=FALSE}
# golf
ggplot(lm(golf$price ~ golf$kilometers), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Audi A3

```{r, message=FALSE, warning=FALSE}
# audi
ggplot(lm(audi$price ~ audi$kilometers), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Skoda Octavia

```{r, message=FALSE, warning=FALSE}
# skoda
ggplot(lm(skoda$price ~ skoda$kilometers), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Volvo XC60

```{r, message=FALSE, warning=FALSE}
# volvo
ggplot(lm(volvo$price ~ volvo$kilometers), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
# toyota
ggplot(lm(toyota$price ~ toyota$kilometers), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```
:::

We can try to fix this using second degree variables. We add vehicle.age squared and kilometers squared as variables to our datasets and run the plots again. Below are the residuals vs fitted value plots of regressions lm(price \~ vehicle.age + vehicle.aged.squared + kilometers + kilometers.squared).

```{r, message=FALSE, warning=FALSE}
# golf
golf$vehicle.age.squared <- (golf$vehicle.age ^ 2)
golf$kilometers.squared <- (golf$kilometers ^ 2)

# audi
audi$vehicle.age.squared <- (audi$vehicle.age ^ 2)
audi$kilometers.squared <- (audi$kilometers ^ 2)

# skoda
skoda$vehicle.age.squared <- (skoda$vehicle.age ^ 2)
skoda$kilometers.squared <- (skoda$kilometers ^ 2)

# volvo
volvo$vehicle.age.squared <- (volvo$vehicle.age ^ 2)
volvo$kilometers.squared <- (volvo$kilometers ^ 2)

# toyota
toyota$vehicle.age.squared <- (toyota$vehicle.age ^ 2)
toyota$kilometers.squared <- (toyota$kilometers ^ 2)
```

::: panel-tabset
### VW Golf

```{r, message=FALSE, warning=FALSE}
# golf
ggplot(lm(golf$price ~ golf$kilometers + golf$kilometers.squared + golf$vehicle.age + golf$vehicle.age.squared), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Audi A3

```{r, message=FALSE, warning=FALSE}
# audi
ggplot(lm(audi$price ~ audi$kilometers + audi$kilometers.squared + audi$vehicle.age + audi$vehicle.age.squared), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Skoda Octavia

```{r, message=FALSE, warning=FALSE}
# skoda
ggplot(lm(skoda$price ~ skoda$kilometers + skoda$kilometers.squared + skoda$vehicle.age + skoda$vehicle.age.squared), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Volvo XC60

```{r, message=FALSE, warning=FALSE}
# volvo
ggplot(lm(volvo$price ~ volvo$kilometers + volvo$kilometers.squared + volvo$vehicle.age + volvo$vehicle.age.squared), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()

```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
# toyota
ggplot(lm(toyota$price ~ toyota$kilometers + toyota$kilometers.squared + toyota$vehicle.age + toyota$vehicle.age.squared), aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()
```
:::

These plots look much better than the ones before. We still notice heteroskedasticity in the errors, especially for the Audis and Volvos.

We need to do a little bit more data wrangling for this question. We need to transform our columns body.type, fuel.type, transmission and drivetrain into logical variables, in order to be able to use them in our regression model.

```{r, message=FALSE, warning=FALSE, results='hide'}
### golf

# For body.type, we can see that the majority of cars are either "Limousine", "Break" or "Cabriolet".
# We will then create a logical column "wagon" which will be set to TRUE where body.type == "Break" is TRUE (Note: "break" is a reserved word). We do the same for columns "cabriolet", "small.car" and "coupe". When all 4 are FALSE, the body.type will be Limousine.

table(golf$body.type)

golf$wagon <- golf$body.type == "Break"
golf$cabriolet <- golf$body.type == "Cabriolet"
golf$small.car <- golf$body.type == "Petite voiture"
golf$coupe <- golf$body.type == "Coupé"

# We will repeat the process for fuel.type. Columns will be "diesel", "hybrid", "natural.gas" and "electric"

golf$diesel <- golf$fuel.type == "Diesel"
golf$hybrid <- ifelse(golf$fuel.type == "Hybride léger essence/électrique" | 
                      golf$fuel.type == "Hybride rechargeable essence/électrique", 
                    TRUE, FALSE)
golf$natural.gas <- golf$fuel.type == "Gaz naturel (CNG) / Essence"
golf$electric <- golf$fuel.type == "Électrique"

# We repeat the process for transmission. We will only have one variable "manual". We consider "Boîte manuelle automatisée" to be automatic because it is very similar to an automatic transmission.

golf$manual <- ifelse(golf$transmission == "Automatique" |
                        golf$transmission == "Boîte manuelle automatisée" |
                        golf$transmission == "Boîte automatique variable", 
                      FALSE, TRUE)

# We repeat the process for drivetrain. We will create one column "awd". We will neglect "Propulsion" and leave it as false, the same as for "Traction avant" because there are only 2 observations.

golf$awd <- golf$drivetrain == "4 roues motrices"

### audi

# For body.type, we can see that the majority of cars are either "Limousine", "Break" or "Cabriolet".
# We will then create a logical column "wagon" which will be set to TRUE where body.type == "Break" is TRUE (Note: "break" is a reserved word). We do the same for columns "cabriolet", "small.car" and "coupe". When all 4 are FALSE, the body.type will be Limousine.

table(audi$fuel.type)

audi$wagon <- audi$body.type == "Break"
audi$cabriolet <- audi$body.type == "Cabriolet"
audi$small.car <- audi$body.type == "Petite voiture"
audi$coupe <- audi$body.type == "Coupé"

# We will repeat the process for fuel.type. Columns will be "diesel", "hybrid", "natural.gas" and "electric"

audi$diesel <- audi$fuel.type == "Diesel"
audi$hybrid <- ifelse(audi$fuel.type == "Hybride léger essence/électrique" | 
                        audi$fuel.type == "Hybride rechargeable essence/électrique" |
                        audi$fuel.type == "Hybride léger diesel/électrique", 
                      TRUE, FALSE)
audi$natural.gas <- audi$fuel.type == "Gaz naturel (CNG) / Essence"
audi$electric <- audi$fuel.type == "Électrique"

# We repeat the process for transmission. We will only have one variable "manual". We consider "Boîte manuelle automatisée" to be automatic because it is very similar to an automatic transmission.

audi$manual <- ifelse(audi$transmission == "Automatique" |
                        audi$transmission == "Boîte manuelle automatisée" |
                        audi$transmission == "Boîte automatique variable", 
                      FALSE, TRUE)

# We repeat the process for drivetrain. We will create one column "awd".

audi$awd <- audi$drivetrain == "4 roues motrices"

### skoda

# For body.type, we can see that the majority of cars are "Break".
# We will then create a logical column "cabriolet" which will be set to TRUE where body.type == "cabriolet" is TRUE. We do the same for column "suv" and "sedan". When the 3 are FALSE, the body.type will be Break.

table(skoda$body.type)

skoda$cabriolet <- skoda$body.type == "Cabriolet"
skoda$suv <- skoda$body.type == "SUV / Tout-terrain"
skoda$sedan <- skoda$body.type == "Limousine"

# We will repeat the process for fuel.type. Columns will be "diesel", "hybrid", and "natural.gas".

skoda$diesel <- skoda$fuel.type == "Diesel"
skoda$hybrid <- ifelse(skoda$fuel.type == "Hybride léger essence/électrique" | 
                        skoda$fuel.type == "Hybride rechargeable essence/électrique" |
                        skoda$fuel.type == "Hybride léger diesel/électrique", 
                      TRUE, FALSE)
skoda$natural.gas <- skoda$fuel.type == "Gaz naturel (CNG) / Essence"

# We repeat the process for transmission. We will only have one variable "manual". We consider "Boîte manuelle automatisée" to be automatic because it is very similar to an automatic transmission.

skoda$manual <- ifelse(skoda$transmission == "Automatique" |
                        skoda$transmission == "Boîte manuelle automatisée" |
                        skoda$transmission == "Boîte automatique variable", 
                      FALSE, TRUE)

# We repeat the process for drivetrain. We will create one column "awd".

skoda$awd <- skoda$drivetrain == "4 roues motrices"

### volvo

# For body.type, we can see that the majority of cars are "SUV / Tout-terrain", we have a very small amount that are other body types. These are errors, the XC60 only comes as an SUV.

table(volvo$drivetrain)

# We will create a logical column "diesel" which will be set to TRUE where fuel.type == "Diesel" is TRUE. We do the same for column "hybrid". When both are FALSE, the fuel.type will be petrol.

volvo$diesel <- volvo$fuel.type == "Diesel"
volvo$hybrid <- ifelse(volvo$fuel.type == "Hybride léger essence/électrique" | 
                        volvo$fuel.type == "Hybride rechargeable essence/électrique" |
                        volvo$fuel.type == "Hybride léger diesel/électrique", 
                      TRUE, FALSE)

# We repeat the process for transmission. We will only have one variable "manual". We consider "Boîte manuelle automatisée" to be automatic because it is very similar to an automatic transmission.

volvo$manual <- ifelse(volvo$transmission == "Automatique" |
                        volvo$transmission == "Boîte manuelle automatisée" |
                        volvo$transmission == "Boîte automatique variable", 
                      FALSE, TRUE)

# We repeat the process for drivetrain. We will create one column "fwd".

volvo$fwd <- volvo$drivetrain == "Traction avant"

### toyota

# For body.type, we can see that the majority of cars are either "Limousine" or "Petite voiture".
# We will create a logical column "sedan" which will be set to TRUE where body.type == "Limousine" is TRUE. We do the same for column "coupe". When both are FALSE, the body.type will be "Petite voiture".

table(toyota$drivetrain)

toyota$sedan <- toyota$body.type == "Limousine"
toyota$coupe <- toyota$body.type == "Coupé"

# We will repeat the process for fuel.type. Columns will be "diesel" and "hybrid".

toyota$diesel <- toyota$fuel.type == "Diesel"
toyota$hybrid <- ifelse(toyota$fuel.type == "Hybride léger essence/électrique" | 
                        toyota$fuel.type == "Hybride rechargeable essence/électrique" |
                        toyota$fuel.type == "Hybride léger diesel/électrique" |
                        toyota$fuel.type == "Hybride intégral essence/électrique",
                      TRUE, FALSE)

# We repeat the process for transmission. We will only have one variable "manual". We consider "Boîte manuelle automatisée" to be automatic because it is very similar to an automatic transmission.

toyota$manual <- ifelse(toyota$transmission == "Automatique" |
                        toyota$transmission == "Boîte manuelle automatisée" |
                        toyota$transmission == "Boîte automatique variable", 
                      FALSE, TRUE)

# We repeat the process for drivetrain. We will create one column "awd".

toyota$awd <- toyota$drivetrain == "4 roues motrices"

```

Now we will make a regression model that includes all of our variables then do a stepwise regression (backward) to remove non significant variables.

```{r, message=FALSE, warning=FALSE, results='hide'}
# golf

golf_model1 <- lm(golf$price ~ golf$kilometers + golf$kilometers.squared + golf$vehicle.age + golf$vehicle.age.squared + golf$power + golf$consumption + golf$expertise + golf$warranty + golf$wagon + golf$cabriolet + golf$small.car + golf$coupe + golf$diesel + golf$hybrid + golf$natural.gas + golf$electric + golf$manual + golf$awd)
summary(golf_model1)
golf_model2 <- stepAIC(golf_model1, direction = "backward")
summary(golf_model2)
# cabriolet and consumption are still not significant at an alpha of 0.01, we remove them
# we subset the data first to exclude observations that contain NA
golf <- golf[complete.cases(golf[, c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "expertise", "warranty", "wagon", "diesel", "manual", "awd")]), ]
golf_model3 <- lm(golf$price ~ golf$kilometers + golf$kilometers.squared + golf$vehicle.age + golf$vehicle.age.squared + golf$power + golf$expertise + golf$warranty + golf$wagon + golf$diesel + golf$manual + golf$awd)
summary(golf_model3)
# All of our variables are now significant. This will be our final model

golf$price.residuals <- golf_model3$residuals
golf$pred.price <- golf_model3$fitted.values

# audi

audi_model1 <- lm(audi$price ~ audi$kilometers + audi$kilometers.squared + audi$vehicle.age + audi$vehicle.age.squared + audi$power + audi$consumption + audi$expertise + audi$warranty + audi$wagon + audi$cabriolet + audi$small.car + audi$coupe + audi$diesel + audi$hybrid + audi$natural.gas + audi$electric + audi$manual + audi$awd)
summary(audi_model1)
# we subset the data first to exclude observations that contain NA
audi <- audi[complete.cases(audi[, c('kilometers', 'kilometers.squared', 'vehicle.age', 'vehicle.age.squared', 'power', 'consumption', 'expertise', 'warranty', 'wagon', 'cabriolet', 'small.car', 'coupe', 'diesel', 'hybrid', 'natural.gas', 'electric', 'manual', 'awd')]), ]
audi_model2 <- stepAIC(audi_model1, direction = "backward")
summary(audi_model2)
# All of our variables are now significant. This will be our final model

audi$price.residuals <- audi_model2$residuals
audi$pred.price <- audi_model2$fitted.values

# skoda

skoda_model1 <- lm(skoda$price ~ skoda$kilometers + skoda$kilometers.squared + skoda$vehicle.age + skoda$vehicle.age.squared + skoda$power + skoda$consumption + skoda$expertise + skoda$warranty + skoda$sedan + skoda$cabriolet + skoda$suv + skoda$diesel + skoda$hybrid + skoda$natural.gas + skoda$manual + skoda$awd)
summary(skoda_model1)
skoda_model2 <- stepAIC(skoda_model1, direction = "backward")
summary(skoda_model2)
# cabriolet and consumption are still not significant at an alpha of 0.01, we remove them
# we subset the data first to exclude observations that contain NA
skoda <- skoda[complete.cases(skoda[, c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "consumption", "expertise", "warranty", "diesel", "manual", "awd")]), ]
skoda_model3 <- lm(skoda$price ~ skoda$kilometers + skoda$kilometers.squared + skoda$vehicle.age + skoda$vehicle.age.squared + skoda$power + skoda$expertise + skoda$warranty + skoda$consumption + skoda$diesel + skoda$manual + skoda$awd)
summary(skoda_model3)
# we remove consumption as it is no longer significant
skoda_model3 <- lm(skoda$price ~ skoda$kilometers + skoda$kilometers.squared + skoda$vehicle.age + skoda$vehicle.age.squared + skoda$power + skoda$expertise + skoda$warranty + skoda$diesel + skoda$manual + skoda$awd)
summary(skoda_model3)
# All of our variables are now significant. This will be our final model

skoda$price.residuals <- skoda_model3$residuals
skoda$pred.price <- skoda_model3$fitted.values

# volvo

volvo_model1 <- lm(volvo$price ~ volvo$kilometers + volvo$kilometers.squared + volvo$vehicle.age + volvo$vehicle.age.squared + volvo$power + volvo$consumption + volvo$expertise + volvo$warranty + volvo$diesel + volvo$hybrid + volvo$manual + volvo$fwd)
summary(volvo_model1)
# we subset the data first to exclude observations that contain NA
volvo <- volvo[complete.cases(volvo[, c('price', 'kilometers', 'kilometers.squared', 'vehicle.age', 'vehicle.age.squared', 'power', 'consumption', 'expertise', 'warranty', 'diesel', 'hybrid', 'manual', 'fwd')]), ]
volvo_model2 <- stepAIC(volvo_model1, direction = "backward")
summary(volvo_model2)
# manual is still not significant at an alpha of 0.01, we remove it
volvo_model3 <- lm(volvo$price ~ volvo$kilometers + volvo$kilometers.squared + volvo$vehicle.age + volvo$vehicle.age.squared + volvo$power + volvo$consumption + volvo$hybrid)
summary(volvo_model3)
# All of our variables are now significant. This will be our final model
volvo$price.residuals <- volvo_model3$residuals
volvo$pred.price <- volvo_model3$fitted.values

# toyota

toyota_model1 <- lm(toyota$price ~ toyota$kilometers + toyota$kilometers.squared + toyota$vehicle.age + toyota$vehicle.age.squared + toyota$power + toyota$consumption + toyota$expertise + toyota$warranty + toyota$sedan + toyota$coupe + toyota$diesel + toyota$hybrid + toyota$manual + toyota$awd)
summary(toyota_model1)
toyota_model2 <- stepAIC(toyota_model1, direction = "backward")
summary(toyota_model2)
# warranty, hybrid, and consumption are still not significant at an alpha of 0.01, we remove them
# we subset the data first to exclude observations that contain NA
toyota <- toyota[complete.cases(toyota[, c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "sedan", "manual", "awd")]), ]
toyota_model3 <- lm(toyota$price ~ toyota$kilometers + toyota$kilometers.squared + toyota$vehicle.age + toyota$vehicle.age.squared + toyota$power + toyota$sedan + toyota$manual + toyota$awd)
summary(toyota_model3)
#we remove sedan
toyota_model3 <- lm(toyota$price ~ toyota$kilometers + toyota$kilometers.squared + toyota$vehicle.age + toyota$vehicle.age.squared + toyota$power + toyota$manual + toyota$awd)
summary(toyota_model3)
# All of our variables are now significant. This will be our final model
toyota$price.residuals <- toyota_model3$residuals
toyota$pred.price <- toyota_model3$fitted.values


```

Now we have found our optimal regression models, we can have a look at their summaries and residuals vs fitted values plots.

::: panel-tabset
### VW Golf

```{r, message=FALSE, warning=FALSE}
ggplot(golf_model3, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()
summary(golf_model3)

```

### Audi A3

```{r, message=FALSE, warning=FALSE}
ggplot(audi_model2, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()
summary(audi_model2)
```

### Skoda Octavia

```{r, message=FALSE, warning=FALSE}
ggplot(skoda_model3, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()
summary(skoda_model3)
```

### Volvo XC60

```{r, message=FALSE, warning=FALSE}
ggplot(volvo_model3, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth()
summary(volvo_model3)
```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
ggplot(toyota_model3, aes(x = .fitted, y = .resid)) +
  geom_point(aes(color = factor(toyota$awd))) +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  geom_smooth() +
  labs(color = "AWD")
summary(toyota_model3)
```
:::

The graphs of our residuals vs fitted values look better than the previous ones, with less heteroskedasticity. For the 5 car models that we have researched, the R-Squared values are between 0.90 and 0.94, which we consider to be very good. We still notice quite a high standard error for all vehicles, which decreases the reliability of the predictions and the usefulness of the tool.

Looking at the Toyota plot, we can notice 2 clearly defined clusters, which represent the cars with all wheel drive vs those with front wheel drive. This is not the only difference between these cars that explains the massive average price difference. When looking at the data, we see that there are 2 submodels of the Toyota Yaris; the "normal" Yaris and the new "TOYOTA Yaris 1.6 GR Sport". The Sport Yaris is a new trim of the Yaris and therefore the listings have a higher average price. They also have more horsepower and AWD, both of which are correlated with higher prices.

We now need to check the models for multicollinearity. We can do this by calculating the VIF (Variance Inflation Factors) for our models.

::: panel-tabset
### VW Golf

```{r, message=FALSE, warning=FALSE}

#plotly bar chart with VIFs for each factor for each vehicle

# golf
# data frame
plot_data <- data.frame(Variables = c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "expertise", "warranty", "wagon", "diesel", "manual", "awd"), VIF = vif(golf_model3))

# function to display horizontal line
hline <- function(y = 0, color = "red") {
  list(
    type = "line",
    x0 = 0,
    x1 = 1,
    xref = "paper",
    y0 = y,
    y1 = y,
    line = list(color = color)
  )
}

# plotly

plot <- plot_ly(plot_data, x = ~Variables, y = ~VIF, type = 'bar', 
                marker = list(color = 'grey')) %>%
  layout(shapes = list(hline(5))) |>
                layout(title = "Variance Inflation Factor (VIF) Values",
               xaxis = list(title = "Variables"),
               yaxis = list(title = "VIF"))

# Display the plot
plot
```

### Audi A3

```{r, message=FALSE, warning=FALSE}
# audi
# data frame 
plot_data <- data.frame(Variables = c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "expertise", "warranty", "cabriolet", "diesel", "manual", "awd"), VIF = vif(audi_model2))

# plotly

plot <- plot_ly(plot_data, x = ~Variables, y = ~VIF, type = 'bar', 
                marker = list(color = 'grey')) %>%
  layout(shapes = list(hline(5))) |>
                layout(title = "Variance Inflation Factor (VIF) Values",
               xaxis = list(title = "Variables"),
               yaxis = list(title = "VIF"))

# Display the plot
plot

```

### Skoda Octavia

```{r, message=FALSE, warning=FALSE}
# skoda
# data frame 
plot_data <- data.frame(Variables = c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "expertise", "warranty", "diesel", "manual", "awd"), VIF = vif(skoda_model3))

# plotly

plot <- plot_ly(plot_data, x = ~Variables, y = ~VIF, type = 'bar', 
                marker = list(color = 'grey')) %>%
  layout(shapes = list(hline(5))) |>
                layout(title = "Variance Inflation Factor (VIF) Values",
               xaxis = list(title = "Variables"),
               yaxis = list(title = "VIF"))

# Display the plot
plot

```

### Volvo XC60

```{r, message=FALSE, warning=FALSE}
# volvo
# data frame 
plot_data <- data.frame(Variables = c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "consumption", "hybrid"), VIF = vif(volvo_model3))

# plotly

plot <- plot_ly(plot_data, x = ~Variables, y = ~VIF, type = 'bar', 
                marker = list(color = 'grey')) %>%
  layout(shapes = list(hline(5))) |>
                layout(title = "Variance Inflation Factor (VIF) Values",
               xaxis = list(title = "Variables"),
               yaxis = list(title = "VIF"))

# Display the plot
plot

```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
# toyota
# data frame 
plot_data <- data.frame(Variables = c("kilometers", "kilometers.squared", "vehicle.age", "vehicle.age.squared", "power", "manual", "awd"), VIF = vif(toyota_model3))

# plotly

plot <- plot_ly(plot_data, x = ~Variables, y = ~VIF, type = 'bar', 
                marker = list(color = 'grey')) %>%
  layout(shapes = list(hline(5))) |>
                layout(title = "Variance Inflation Factor (VIF) Values",
               xaxis = list(title = "Variables"),
               yaxis = list(title = "VIF"))

# Display the plot
plot

```
:::

By definition, if a variable has a VIF score of 1, it is completely independent. As a rule of thumb, we consider variables with a VIF between 1 and 5 to be moderately correlated and those with a VIF higher than 5 to be highly correlated. These bar charts show us that for every model, vehicle.age and kilometers are clearly correlated. This is logical because the longer an owner has had a car for, the more days he has used it to travel, and the more kilometers have accumulated on the vehicle. In theory, it is possible to own a car and put very few or no kilometers on it for an extended period of time, as well as put a large amount of kilometers in a short amount of time. These 2 variables are equally of great importance to determine a vehicle's price, and therefore we won't exclude either of them from our model, despite there being severe multicollinearity.

When looking at the Toyota Yaris chart, we see that awd and power also have a high VIF, and we suspect that this is due to the Toyota Yaris Sport, which we saw has a much higher power and price than the others, and is the only Yaris to be AWD.

```{r, message=FALSE, warning=FALSE}

```

```{r, message=FALSE, warning=FALSE}

```
