---
title: "Q2 models"
format:
  html: 
    code-fold: true
editor: visual
---

### Q2. What are the factors that influence the duration of a listing for a used car?

```{r, message=FALSE, warning=FALSE}
# Libraries + datasets

library(tidyverse)
library(plotly)
library(corrplot)
library(Hmisc)
library(car)
library(MASS)
library(kableExtra)
setwd("~/GitHub/Data_science/cleaned-data")
golf <- read.csv("golf_models_data.csv")
audi <- read.csv("audi_models_data.csv")
skoda <- read.csv("skoda_models_data.csv")
volvo <- read.csv("volvo_models_data.csv")
toyota <- read.csv("toyota_models_data.csv")
```

If we first look at the data, we will see an enormous amount of listings on 2022-11-14, which is unrealistic, and most likely an error. We can see this clearly by visualising the frequency of listings by date.

::: panel-tabset
### VW Golf

```{r, message=FALSE, warning=FALSE}
ggplot(golf, aes(x = listing.age)) +
  geom_histogram(binwidth = 3, fill = "skyblue", color = "black") +
  labs(
    title = "Histogram of Listing Duration",
    x = "Listing Duration (Days)",
    y = "Frequency"
  )
```

### Audi A3

```{r, message=FALSE, warning=FALSE}
ggplot(audi, aes(x = listing.age)) +
  geom_histogram(binwidth = 3, fill = "skyblue", color = "black") +
  labs(
    title = "Histogram of Listing Duration",
    x = "Listing Duration (Days)",
    y = "Frequency"
  )
```

### Skoda Octavia

```{r, message=FALSE, warning=FALSE}
ggplot(skoda, aes(x = listing.age)) +
  geom_histogram(binwidth = 3, fill = "skyblue", color = "black") +
  labs(
    title = "Histogram of Listing Duration",
    x = "Listing Duration (Days)",
    y = "Frequency"
  )
```

### Volvo XC60

```{r, message=FALSE, warning=FALSE}
ggplot(volvo, aes(x = listing.age)) +
  geom_histogram(binwidth = 3, fill = "skyblue", color = "black") +
  labs(
    title = "Histogram of Listing Duration",
    x = "Listing Duration (Days)",
    y = "Frequency"
  )
```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
ggplot(toyota, aes(x = listing.age)) +
  geom_histogram(binwidth = 3, fill = "skyblue", color = "black") +
  labs(
    title = "Histogram of Listing Duration",
    x = "Listing Duration (Days)",
    y = "Frequency"
  )
```
:::

When inspecting the listings one by one, we saw that this is not a scraping error, and this is really the data found on AutoScout24.ch. A possible explanation would be that all listings before this date have taken as a value this date. Regardless of the reason, we can safely assume that this doesn't represent reality, so to prevent this from biasing our models, we will remove all observations with created.date set at 2022-11-14.

```{r, message=FALSE, warning=FALSE}
golf <- subset(golf, created.date != "2022-11-14")
audi <- subset(audi, created.date != "2022-11-14")
skoda <- subset(skoda, created.date != "2022-11-14")
volvo <- subset(volvo, created.date != "2022-11-14")
toyota <- subset(toyota, created.date != "2022-11-14")
```

```{r, message=FALSE, warning=FALSE}

```

```{r, message=FALSE, warning=FALSE}

```

```{r, message=FALSE, warning=FALSE}

```

Our dependant variable will be listing.age. We will make a regression model that includes all of our variables then remove non significant variables, in order to find the optimal model.

```{r, message=FALSE, warning=FALSE, results='hide'}
# golf

golf_model1 <- lm(golf$listing.age ~ golf$price + golf$price.residuals + golf$kilometers + golf$kilometers.squared + golf$vehicle.age + golf$vehicle.age.squared + golf$power + golf$consumption + golf$expertise + golf$warranty + golf$wagon + golf$cabriolet + golf$small.car + golf$coupe + golf$diesel + golf$hybrid + golf$natural.gas + golf$electric + golf$manual + golf$awd)
summary(golf_model1)
# No variable is significant at alpha = 0.01 except manual, let's test a simple linear model with manual
golf_model1 <- lm(golf$listing.age ~ golf$manual)
summary(golf_model1)
# No variable is significant

# audi

audi_model1 <- lm(audi$listing.age ~ audi$price + audi$price.residuals + audi$kilometers + audi$kilometers.squared + audi$vehicle.age + audi$vehicle.age.squared + audi$power + audi$consumption + audi$expertise + audi$warranty + audi$wagon + audi$cabriolet + audi$small.car + audi$coupe + audi$diesel + audi$hybrid + audi$natural.gas + audi$electric + audi$manual + audi$awd)
summary(audi_model1)
# we notice again that no variables are significant at alpha = 0.01

# skoda

skoda_model1 <- lm(skoda$listing.age ~ skoda$price + skoda$price.residuals + skoda$kilometers + skoda$kilometers.squared + skoda$vehicle.age + skoda$vehicle.age.squared + skoda$power + skoda$consumption + skoda$expertise + skoda$warranty + skoda$sedan + skoda$cabriolet + skoda$suv + skoda$diesel + skoda$hybrid + skoda$natural.gas + skoda$manual + skoda$awd)
summary(skoda_model1)
# No variable is significant at alpha = 0.01 except sedan, let's test a simple linear model with sedan
skoda_model1 <- lm(skoda$listing.age ~ skoda$sedan)
summary(skoda_model1)
# we notice again that no variables are significant at alpha = 0.01

# volvo

volvo_model1 <- lm(volvo$listing.age ~ volvo$price + volvo$price.residuals + volvo$kilometers + volvo$kilometers.squared + volvo$vehicle.age + volvo$vehicle.age.squared + volvo$power + volvo$consumption + volvo$expertise + volvo$warranty + volvo$diesel + volvo$hybrid + volvo$manual + volvo$fwd)
summary(volvo_model1)
# No variable is significant at alpha = 0.01 except expertise, let's test a simple linear model with expertise
volvo_model1 <- lm(volvo$listing.age ~ volvo$expertise)
summary(volvo_model1)
# expertise is significant, but the R squared is very low (0.014), we don't consider this to be a good model.



# toyota

toyota_model1 <- lm(toyota$listing.age ~ toyota$price + toyota$price.residuals + toyota$kilometers + toyota$kilometers.squared + toyota$vehicle.age + toyota$vehicle.age.squared + toyota$power + toyota$consumption + toyota$expertise + toyota$warranty + toyota$sedan + toyota$coupe + toyota$diesel + toyota$hybrid + toyota$manual + toyota$awd)
summary(toyota_model1)
# No variable is significant at alpha = 0.01 except expertise, let's test a simple linear model with expertise
toyota_model1 <- lm(toyota$listing.age ~ toyota$price.residuals)
summary(toyota_model1)
# expertise is significant, but the R squared is very low (0.025), we don't consider this to be a good model.



```

It looks like almost none of the cars' attributes can explain differences in listing ages. We have only managed to find 2 simple linear models with a significant variable for the Volvos and Toyotas, but looking at the plots below, we can see they aren't very useful because the R squared values are very low.

::: panel-tabset
### Volvo XC60

```{r, message=FALSE, warning=FALSE}
ggplot(volvo, aes(listing.age, expertise)) + 
  geom_point() +
  ggtitle("Plot of listing age vs expertise")
summary(volvo_model1)
```

### Toyota Yaris

```{r, message=FALSE, warning=FALSE}
ggplot(toyota, aes(listing.age, price.residuals)) + 
  geom_point() +
  geom_smooth(method = lm) +
  ylim(min(toyota$price.residuals), max(toyota$price.residuals)) +
  ggtitle("Plot of listing age vs price residuals")
summary(toyota_model1)

```
:::
