---
title: "EDA"
format: html
editor: visual
---


# Exploratory data analysis

```{r, message = FALSE, warning=FALSE}
source(here::here("scripts/setup.R"))
```


```{r echo=FALSE, message=FALSE, results='hide'}
# Chargement des bibliothèques nécessaires
library(ggplot2)
library(dplyr)
library(plotly)
library(htmltools)
library(formattable)
library(gridExtra)
library(htmltools)
library(shiny)
library(tidyverse)
library(patchwork)
```

## Explanatory Variable Analysis: Impact of Physical Factors on Used Car Prices

### Histograms of prices distributions

<p align="justify">
As part of our exploratory data analysis, we opted for visualizations focusing on the price distribution of the different vehicles (Volvo, Toyota, Skoda, Golf, Audi) present in our datasets. To do this, we used the ggplot2 library to create price distribution histograms, enriched with density curves for a better appreciation of the distribution. For greater interactivity, we then integrated the plotly library, making it easier to observe the concentration of cars at similar prices. These histograms, enriched with density curves, provide a clear perspective on price distribution, highlighting the most frequent price ranges and anomalies.
<p>

::: panel-tabset

## Volvo
```{r}
#| label: load-packages
#| warning: false


golf <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/golf2_cleaned.csv")
skoda <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/skoda2_cleaned.csv")
audi <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/audi2_cleaned.csv")
toyota <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/toyota_cleaned.csv")
volvo <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/volvo2_cleaned.csv")

# Combiner tous les datasets en un seul dataframe
data <- rbind(golf, skoda, audi, toyota, volvo)


# Création d'une fonction pour tracer un histogramme de distribution des prix
plot_price_distribution <- function(data, title) {
   p <- ggplot(data, aes(x = price))  + 
     geom_histogram(aes(y = ..density..), bins = 30, fill = "#8B94F6", color = "darkblue") +
    geom_density(color = "darkblue", size = 1) +
    theme_minimal() +
    labs(title = paste("Distribution des prix pour", title), x = "Prix", y = "Density")
   ggplotly(p)
}
volvo_plot <- plot_price_distribution(volvo, "Volvo")
volvo_plot
```
-Volvo has an average price of CHF 39,811, with a range from CHF 5,500 to CHF 94,900. This wide price range suggests a diversified Volvo offering, covering different market segments.

## Toyota 
```{r}
toyota_plot <- plot_price_distribution(toyota, "Toyota")
toyota_plot
```

-Toyota is positioned at an average price of CHF 14,872, ranging from CHF 400 to CHF 80,000. Its down-market price distribution reflects Toyota's reputation for affordable, reliable vehicles.

## Skoda
```{r}
skoda_plot <- plot_price_distribution(skoda, "Skoda")
skoda_plot
```
-Skoda has an average price of CHF 18,961, ranging from CHF 300 to CHF 59,900. This distribution, close to that of Toyota, indicates that Skoda targets mainly the economy and mid-range segments.

## Golf
```{r}
golf_plot <- plot_price_distribution(golf, "Golf")
golf_plot
```
-The Golf has an average price of CHF 19,398, ranging from CHF 350 to CHF 59,990. Its extensive distribution shows a diversity of models, targeting a wide spectrum of customers, from the most frugal to the most demanding.

## Audi 
```{r}
audi_plot <- plot_price_distribution(audi, "Audi")
audi_plot
```
-Audi, with an average price of CHF 20,928 and a range from CHF 600 to CHF 66,500, shows an extensive distribution, with a notable presence in the high-end segment, in line with its positioning as a premium brand.

:::

<p align="justify">
Through our visualizations, we have identified striking price differentials between brands, revealing the influence of multiple factors on the used car market, which we will analyze in detail later. These data raise interesting questions about the perceived value of brands and their market positioning:
<p>


<p align="justify">
This approach not only allowed us to observe the price distribution for each type of car but also to understand the price variations by brand in the used car market. Furthermore, this visualization guided our analysis towards a detailed exploration of the factors that may influence these price fluctuations.
<p>

### Brands comparisons

<p align="justify">
The bar chart below illustrates the average price of cars by brand, depending on the date of manufacture. To create this visualization, we used the ggplot2 library, then transformed it into an interactive graph using ggplotly. By merging all the data sets into one, we obtained a global view for different brands. This approach enables us to compare directly how the year of manufacture influences the market price of used cars of different makes.
</p>

```{r}


# Combinez tous les dataframes en un seul pour faciliter la visualisation
combined_df <- rbind(
  transform(volvo, Brand = 'Volvo'),
  transform(toyota, Brand = 'Toyota'),
  transform(skoda, Brand = 'Skoda'),
  transform(golf, Brand = 'Golf'),
  transform(audi, Brand = 'Audi')
)

# Graphique en barres pour le prix moyen en fonction de l'année
graph <- ggplot(combined_df, aes(x = date, y = price, fill = Brand)) +
  geom_bar(stat = "summary", fun = mean) +
  labs(title = "Prix moyen par marque et année", x = "Année de fabrication", y = "Prix moyen") +
  theme_minimal()

p1 <- ggplotly(graph)
p1
```

<p align="justify">
As can be seen from the bar chart, the more recent the car, the higher the price, regardless of brand. However, it is interesting to note that Audi and Golf are generally more expensive than Skoda, Toyota or Volvo.

Understanding this graph has enabled us to visualize the impact of a car's date of manufacture on its selling price on the second-hand market. This variation could also be explained by other factors, such as technological developments in fuel or wear and tear on older cars.
<p>

### Body type and price

<p align="justify">
This box plot enabled us to understand the different prices according to body type for the different makes of car. To do this, we used the ggplot2 library, complemented by the interactivity of plotly. The choice of visualition was motivated by its ability to effectively show the price distribution, including median, quartiles and outliers. In addition, the colors of the plot boxes assigned to a car brand highlight the type of bodywork offered by the different brands.
<p>

```{r}


# Assuming you've loaded your datasets into dataframes named volvo_data, toyota_data, skoda_data, golf_data, audi_data

# Combine all dataframes into one
all_cars <- bind_rows(
  mutate(volvo, brand = "Volvo"),
  mutate(toyota, brand = "Toyota"),
  mutate(skoda, brand = "Skoda"),
  mutate(golf, brand = "Golf"),
  mutate(audi, brand = "Audi")
)

# Convert body type to a factor for better plotting
all_cars$body.type <- as.factor(all_cars$body.type)

# Create the scatter plot
graph0 <- ggplot(all_cars, aes(x = body.type, y = price, fill = brand)) +
  geom_boxplot() +
  labs(title = "Price distribution by body type and brand",
       x = "body type", y = "Price") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotation des étiquettes de l'axe X pour une meilleure lisibilité

p1 <- ggplotly(graph0)

p1


# Note: geom_smooth is used here with method = "lm" which fits a linear model to the data. 
# The 'se = FALSE' argument disables the display of the confidence interval around the smooth line.

# box plot 

```

<p align="justify">
-   Other: This category, encompassing various vehicle types, shows a wide price range. Audi and Volvo stand out with higher median prices, probably reflecting a range of high-end or specialist models.

-   Station wagon: Station wagons of all makes show a fairly uniform price distribution, suggesting a degree of price stability in this body segment.

-   Cabriolet: Cabriolets, particularly from Audi and Volvo, are characterized by higher median prices, suggesting upmarket positioning or luxury features.

-   Coupé: The coupé category displays a wide range of prices, with Volvo leading the way in terms of median, which could indicate superior quality or specialization.

-   Limousine: Limousines show a diversity of prices, with less dispersion at Skoda and Toyota, which could reflect a more standardized offering or competitive pricing.

-   MPV / Minibus: In this category, Skoda and Toyota stand out with lower median prices, suggesting more affordable options.

-   Small car: Skoda and Toyota's small cars have lower median prices, in keeping with their image as brands offering economical vehicles.

-   SUV / Off-road: SUVs and off-road vehicles present a wide price range, with Audi and Volvo having higher medians, consistent with their status as luxury brands.
<p>

<p align="justify">
The box chart revealed more nuanced insights, such as the existence of significant price variability within the same brands according to body type. The box plot has also given us a better understanding of brand trends, and can once again highlight their positioning.
<p>

### summary tables for prices

<p align="justify">
We have chosen to summarize vehicle price data through basic descriptive statistics: mean, median and standard deviation. These measures were calculated for each vehicle brand in our dataset. To visualize these statistics, we created a summary table using the formattable library in R, which offers an attractive and intuitive visual representation of numerical data.
<p>

```{r}

# Fonction pour calculer les statistiques de base
calculate_stats <- function(df) {
  df %>%
    summarise(
      Moyenne = mean(price, na.rm = TRUE),
      Médiane = median(price, na.rm = TRUE),
      Ecart_Type = sd(price, na.rm = TRUE)
    )
}

# Calcul des statistiques pour chaque marque
stats_volvo <- calculate_stats(volvo)
stats_toyota <- calculate_stats(toyota)
stats_skoda <- calculate_stats(skoda)
stats_golf <- calculate_stats(golf)
stats_audi <- calculate_stats(audi)

# Création d'un tableau récapitulatif
summary_table <- rbind(
  Volvo = stats_volvo,
  Toyota = stats_toyota,
  Skoda = stats_skoda,
  Golf = stats_golf,
  Audi = stats_audi
)

# Mise en forme du tableau avec formattable
color_formatter <- color_tile("white", "lightblue")
formattable(summary_table, list(
  Moyenne = color_formatter,
  Médiane = color_formatter,
  Ecart_Type = color_formatter
))



```

<p align="justify">
Volvo shows the highest average and median prices, suggesting a more premium pricing strategy compared to the other brands. Toyota stands out with significantly lower average and median prices, aligning with its market positioning as an affordable and reliable car brand. Skoda, Golf, and Audi have relatively similar average prices, but Audi tends to be slightly more expensive on average. The standard deviation values indicate the variability in pricing within each brand. Volvo shows the highest variability, suggesting a wide range of models from more affordable to high-end. Toyota, with a lower standard deviation, indicates more consistent pricing across its range.
<p>

### Mileage (Kilometers) and Its Impact on Price

<p align="justify">
For this relationship, we chose to use a scatterplot, which we generated using the ggplot2 library and ggplotly for interactivity. The decision to use scatterplots was based on the need to understand the nature of the relationship between mileage and price. The choice of distinct colors for each car facilitates visualization and comparison between brands.
<p>

::: panel-tabset
## Audi

```{r}
# Enhancing the scatter plots

# AUDI: Mileage vs Price
graph1 <- ggplot(audi, aes(x = kilometers, y = price)) +
  geom_point(color = "#C0C0C0", size = 1, alpha = 0.6) +
  labs(title = "Audi: Mileage vs Price", x = "Mileage", y = "Price") +
  theme_classic()
p1 <- ggplotly(graph1)
p1
```

## Golf

```{r}

# GOLF: Mileage vs Price
graph2 <- ggplot(golf, aes(x = kilometers, y = price)) +
  geom_point(color = "#1E90FF", size = 1, alpha = 0.6) +
  labs(title = "Golf: Mileage vs Price", x = "Mileage", y = "Price") +
  theme_classic()
p2 <- ggplotly(graph2)
p2

```

## Toyota

```{r}
# TOYOTA: Mileage vs Price
graph3 <- ggplot(toyota, aes(x = kilometers, y = price)) +
  geom_point(color = "#FF0000", size = 1, alpha = 0.6) +
  labs(title = "Toyota: Mileage vs Price", x = "Mileage", y = "Price") +
  theme_classic()
p3 <- ggplotly(graph3)
p3
```

## Skoda

```{r}
# SKODA: Mileage vs Price
graph4 <- ggplot(skoda, aes(x = kilometers, y = price)) +
  geom_point(color = "#006400", size = 1, alpha = 0.6) +
  labs(title = "Skoda: Mileage vs Price", x = "Mileage", y = "Price") +
  theme_classic()
p4 <- ggplotly(graph4)
p4
```

## Volvo

```{r}
# VOLVO: Mileage vs Price
graph5 <- ggplot(volvo, aes(x = kilometers, y = price)) +
  geom_point(color = "#000080", size = 1, alpha = 0.6) +
  labs(title = "Volvo: Mileage vs Price", x = "Mileage", y = "Price") +
  theme_classic()
p5 <- ggplotly(graph5)
p5
```
:::

<p align="justify">
By analyzing the graphs, we have observed that, for some brands, price decreases significantly with increasing mileage, while for others, the impact of mileage on price is less pronounced. This reflects the fact that, while mileage can have an impact on price, other factors can also explain consumer choices.
<p>

### Engine Power (Power) and Price Correlation
<p align="justify">
The use of scatter graphs aims to visualize the impact of engine power on sales prices, and whether this trend varies from one brand to another on the used car market.
<p>

::: panel-tabset
## Audi

```{r}
# AUDI: Engine Power vs Price
graph1 <- ggplot(audi, aes(x = power, y = price)) +
  geom_point(color = "red", size = 0.5, alpha = 0.6) +
  labs(title = "Audi: Engine Power vs Price", x = "Engine Power (HP)", y = "Price") +
  theme_minimal()
p1 <- ggplotly(graph1)
p1
```

## Toyota

```{r}
# TOYOTA: Engine Power vs Price
graph2 <- ggplot(toyota, aes(x = power, y = price)) +
  geom_point(color = "green", size = 0.5, alpha = 0.6) +
  labs(title = "Toyota: Engine Power vs Price", x = "Engine Power (HP)", y = "Price") +
  theme_minimal()
p2 <- ggplotly(graph2)
p2
```

## Skoda

```{r}
# SKODA: Engine Power vs Price
graph3 <- ggplot(skoda, aes(x = power, y = price)) +
  geom_point(color = "purple", size = 0.5, alpha = 0.6) +
  labs(title = "Skoda: Engine Power vs Price", x = "Engine Power (HP)", y = "Price") +
  theme_minimal()
p3 <- ggplotly(graph3)
p3
```

## Golf

```{r}
# GOLF: Engine Power vs Price
graph4 <- ggplot(golf, aes(x = power, y = price)) +
  geom_point(color = "blue", size = 0.5, alpha = 0.6) +
  labs(title = "Golf: Engine Power vs Price", x = "Engine Power (HP)", y = "Price") +
  theme_minimal()
p4 <- ggplotly(graph4)
p4
```

## Volvo

```{r}
# VOLVO: Engine Power vs Price
graph5 <- ggplot(volvo, aes(x = power, y = price)) +
  geom_point(color = "orange", size = 0.5, alpha = 0.6) +
  labs(title = "Volvo: Engine Power vs Price", x = "Engine Power (HP)", y = "Price") +
  theme_minimal()
p5 <- ggplotly(graph5)
p5
```
:::

<p align="justify">
The data suggests a positive correlation between engine power and car price. Higher-powered cars, often offering better performance, command higher prices. This trend is particularly pronounced in brands known for their performance-oriented models like Audi, Golf and toyota.
<p>

### Influence of Fuel Type on Car Pricing
<p align="justify">
Different fuel types cater to various market segments and preferences. To visualize how fuel type influences car prices, average prices for different fuel types were plotted in bar charts for each brand
<p>

::: panel-tabset

## Audi

```{r}
# Chargement des données
audi <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/audi_models_data.csv")
golf <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/golf_models_data.csv")
toyota <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/toyota_models_data.csv")
skoda <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/skoda_models_data.csv")
volvo <- read.csv("~/Downloads/Data_science-main-2/cleaned-data/volvo_models_data.csv")

# Fonction pour ajuster les données et créer le graphique en barres
create_bar_plot <- function(data, title) {
  data %>%
    mutate(fuel.type = ifelse(grepl("hybrid", fuel.type, ignore.case = TRUE), "hybrid", fuel.type)) %>%  # Regroupe tous les types d'hybrides
    group_by(fuel.type) %>%
    summarize(Average_Price = mean(price, na.rm = TRUE)) %>%
    ggplot(aes(x = fuel.type, y = Average_Price, fill = fuel.type)) +
    geom_col() +
    scale_fill_manual(values = c("Diesel" = "blue", "Essence" = "red", "hybrid" = "green", "Electrique" = "violet", "Gaz naturel (CNG) /Essence " = "orange")) +
    labs(title = title, x = "Type de Carburant", y = "Prix Moyen") +
    theme_minimal()
}

# Création des graphiques pour chaque marque
plot_audi <- create_bar_plot(audi, "AUDI - Fuel type vs Average price ")

p1 <- ggplotly(plot_audi)
p1
```

## Golf
```{r}
plot_golf <- create_bar_plot(golf, "GOLF - Fuel type vs Average price ")
p2 <- ggplotly(plot_golf)
p2
```

## Toyota 
```{r}
plot_toyota <- create_bar_plot(toyota, "TOYOTA - Fuel type vs Average price ")
p3 <- ggplotly(plot_toyota)
p3
```

## Skoda 
```{r}
plot_skoda <- create_bar_plot(skoda, "SKODA - Fuel type vs Average price ")
p4 <- ggplotly(plot_skoda)
p4
```

## Volvo
```{r}
plot_volvo <- create_bar_plot(volvo, "VOLVO - Fuel type vs Average price ")
p5 <- ggplotly(plot_volvo)
p5
```
:::


<p align="justify">
The charts reveal significant price disparities based on fuel type, with hybrids and electric vehicles often priced higher. These differences are brand-specific and reflect the brand's technological focus and market positioning in terms of fuel technology.
<p>

### Year of Manufacture and Its Effect on Pricing

<p align="justify">
The year a car was manufactured can provide insights into its technological relevance and condition. Bar charts depicting the average price per year for each brand were analyzed
<p> 

::: panel-tabset
## Audi 

```{r, warning=FALSE}
## proposition 2 : en fonction de l'année de fabrication 
graph.1 <- ggplot(audi, aes(x = date, y = price)) +
  geom_violin(trim = FALSE, fill = "skyblue", alpha = 0.7) +
  geom_jitter(width = 0.2, color = "darkblue", size = 1, alpha = 0.5) +
  theme_minimal() +
  labs(title = "Audi - Distribution des Prix par Année de Fabrication", x = "Année", y = "Prix")
p.1 <- ggplotly(graph.1)
p.1
```

## Golf 
```{r, warning=FALSE}
graph.2 <- ggplot(golf, aes(x = date, y = price)) +
  geom_violin(trim = FALSE, fill = "skyblue", alpha = 0.7) +
  geom_jitter(width = 0.2, color = "darkblue", size = 1, alpha = 0.5) +
  theme_minimal() +
  labs(title = "Audi - Distribution des Prix par Année de Fabrication", x = "Année", y = "Prix")
p.2 <- ggplotly(graph.2)
p.2
```

## Skoda
```{r, warning=FALSE}
graph.3 <- ggplot(skoda, aes(x = date, y = price)) +
  geom_violin(trim = FALSE, fill = "skyblue", alpha = 0.7) +
  geom_jitter(width = 0.2, color = "darkblue", size = 1, alpha = 0.5) +
  theme_minimal() +
  labs(title = "Audi - Distribution des Prix par Année de Fabrication", x = "Année", y = "Prix")
p.3 <- ggplotly(graph.3)
p.3
```

## Toyota
```{r, warning=FALSE}
graph.4 <- ggplot(toyota, aes(x = date, y = price)) +
  geom_violin(trim = FALSE, fill = "skyblue", alpha = 0.7) +
  geom_jitter(width = 0.2, color = "darkblue", size = 1, alpha = 0.5) +
  theme_minimal() +
  labs(title = "Audi - Distribution des Prix par Année de Fabrication", x = "Année", y = "Prix")
p.4 <- ggplotly(graph.4)
p.4
```

## Volvo
```{r, warning=FALSE}
graph.5 <- ggplot(volvo, aes(x = date, y = price)) +
  geom_violin(trim = FALSE, fill = "skyblue", alpha = 0.7) +
  geom_jitter(width = 0.2, color = "darkblue", size = 1, alpha = 0.5) +
  theme_minimal() +
  labs(title = "Audi - Distribution des Prix par Année de Fabrication", x = "Année", y = "Prix")
p.5 <- ggplotly(graph.5)
p.5
```
::: 
<p align="justify">
Newer models generally have higher average prices, likely due to more advanced technology, better features, and lower mileage. The rate of depreciation over the years varies among brands, with some luxury brands retaining their value longer.
<p>

### Consumption vs price

```{r}
## Proposition 1 : enfonction de l'age du vehicule 

# Calcul de la moyenne des prix pour chaque combinaison année/marque
audi_heatmap_data <- audi %>%
  group_by(consumption) %>%
  summarise(mean_price = mean(price, na.rm = TRUE))

# Création du graphique de chaleur
graph_1 <- ggplot(audi_heatmap_data, aes(x = consumption, y = factor(1), fill = mean_price)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(title = "Audi - Moyenne des Prix par L'age du vehicule", x = "Age", y = "") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())



# Création du graphique de chaleur

# Calcul de la moyenne des prix pour chaque combinaison année/marque
golf_heatmap_data <- golf %>%
  group_by(consumption) %>%
  summarise(mean_price = mean(price, na.rm = TRUE))
graph_2 <- ggplot(golf_heatmap_data, aes(x = consumption, y = factor(1), fill = mean_price)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(title = "golf - Moyenne des Prix par L'age du vehicule", x = "Age", y = "") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())



# Calcul de la moyenne des prix pour chaque combinaison année/marque
volvo_heatmap_data <- volvo %>%
  group_by(consumption) %>%
  summarise(mean_price = mean(price, na.rm = TRUE))
graph_3 <- ggplot(volvo_heatmap_data, aes(x = consumption, y = factor(1), fill = mean_price)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(title = "volvo- Moyenne des Prix par l'age du vehicule", x = "age", y = "") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())



# Calcul de la moyenne des prix pour chaque combinaison année/marque
skoda_heatmap_data <- skoda %>%
  group_by(consumption) %>%
  summarise(mean_price = mean(price, na.rm = TRUE))
graph_4 <- ggplot(skoda_heatmap_data, aes(x = consumption, y = factor(1), fill = mean_price)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(title = "skoda - Moyenne des Prix par l'age du vehicule", x = "age", y = "") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())



# Calcul de la moyenne des prix pour chaque combinaison année/marque
toyota_heatmap_data <- golf %>%
  group_by(consumption) %>%
  summarise(mean_price = mean(price, na.rm = TRUE))
graph_5 <- ggplot(toyota_heatmap_data, aes(x = consumption, y = factor(1), fill = mean_price)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(title = "toyota - Moyenne des Prix par l'age du vehicule", x = "Age", y = "") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())


p_1 <- ggplotly(graph_1)
p_2 <- ggplotly(graph_2)
p_3 <- ggplotly(graph_3)
p_4 <- ggplotly(graph_4)
p_5 <- ggplotly(graph_5)

# Générer les boutons et le conteneur pour les graphiques
buttons <- tagList(
  tags$button("Audi", onclick = "showPlot('audi')", class = "btn btn-default"),
  tags$button("Golf", onclick = "showPlot('golf')", class = "btn btn-default"),
  tags$button("Volvo", onclick = "showPlot('volvo')", class = "btn btn-default"),
  tags$button("Skoda", onclick = "showPlot('skoda')", class = "btn btn-default"),
  tags$button("Toyota", onclick = "showPlot('toyota')", class = "btn btn-default")
)

plot_containers <- tagList(
  tags$div(id = "audi", style = "display:none;", p_1),
  tags$div(id = "golf", style = "display:none;", p_2),
  tags$div(id = "volvo", style = "display:none;", p_3),
  tags$div(id = "skoda", style = "display:none;", p_4),
  tags$div(id = "toyota", style = "display:none;", p_5)
)

# Combiner les boutons et les conteneurs
html_output <- tagList(buttons, plot_containers)

# Ajouter le code JavaScript
js_code <- HTML("
<script>
  function showPlot(plotId) {
    var plots = ['audi', 'golf', 'volvo', 'skoda', 'toyota'];
    plots.forEach(function(id) {
      var plotEl = document.getElementById(id);
      if (plotEl) {
        plotEl.style.display = 'none';
      }
    });
    var showEl = document.getElementById(plotId);
    if (showEl) {
      showEl.style.display = 'block';
    }
  }
  // Afficher le premier graphique par défaut
  showPlot('audi');
</script>
")

# Afficher l'interface utilisateur
htmltools::tagList(html_output, js_code)



```

